%-------------------------
% Resume in LaTeX - Derived from provided template
% Author: Eli Gregory
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure machine readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}: #2 \vspace{-2pt}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Define 70% gray color
\definecolor{seventyGray}{gray}{0.7}

% Update hyperref style to use 70% gray
\hypersetup{
  colorlinks=true,
  urlcolor=seventyGray
}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {\LARGE \textbf{Eli Gregory}} & \\
  \href{mailto:eligreg@gmail.com}{eligreg@gmail.com} & 301.602.0853 \\
\end{tabular*}

\vspace{5pt}
Well over a decade of iOS development, I've built a wide variety of tasteful apps for companies at all sizes, with a keen product sense, natural design instincts, and deep engineering curiosity. I'm comfortable making sustainable, best-practice decisions, iterating quickly and prioritizing the needs of the business. I obsess on the details and won't ship unless I'm confident in the product. My sweet spot is building apps from 0 to 1.

%-----------IOS-----------------
\section{iOS}
\resumeItemListStart
  \resumeItem{Modern Stack}{Swift, SwiftUI, Swift Concurrency, Swift Packages (modular feature development), Swift Data (local storage), TCA (3rd party architecture: composable \& testable), Xcode Cloud (CI/CD), Swift Testing (unit testing), ViewInspector (3rd party SwiftUI view unit testing), TestFlight (beta distribution), Instruments (app profiling), Xcode \& ChatGPT Plus \& Cursor (accelerated dev, test \& doc writing)}
  \resumeItem{Legacy}{Objective-C, UIKit, MVC, Core Data, Grand Central Dispatch (GCD), Combine, Storyboards, XIBs, CocoaPods, Carthage}
\resumeItemListEnd

%-----------ADDITIONAL PLATFORMS-----------------
\section{Additional Platforms}
\resumeItemListStart
  \resumeItem{GIS \& Mapping}{ArcGIS Maps SDK (Native platforms), ArcGIS Online, ArcGIS API for Python, ArcGIS Pro, Apple MapKit}
  \resumeItem{Web Apps}{Node \& Express JS, Gatsby JS, Ruby on Rails, Python Flask, Python Django}
  \resumeItem{Embedded Systems}{Arduino, Pixel Pusher, Raspberry Pi}
\resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Indiana University}{Bloomington, Indiana}
    {B.S. Informatics @ School of Informatics, Computing and Engineering}{2010}
    \resumeItemListStart
      \item Double Minor: Fine Arts (Graphic Design), Telecommunications
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Freemodel}{Remote}
    {Senior Software Engineer, iOS Client Apps}{July 2022 -- December 2024}
    \resumeItemListStart
      \item Early hire to venture backed Silicon Valley startup, the "Uber for home remodeling" - built, tested and shipped client app from 0 to 1 (feature complete).
      \item Contributed 44.3\% of surviving lines of code for codebase with 5 contributors, over 2.5 years.
      \item Tactfully built foundational infra and established early architectural patterns, balancing velocity with longer term sustainable code.
      \item Directly responsible for three major successful product releases, supplanting business operations from manual spreadsheets to automated digital platform (the company moat).
      \item Led tech eval of Skip.tools, a Swift \& SwiftUI to Kotlin \& Jetpack Compose transpiler for cross platform app development.
    \resumeItemListEnd
  \href{https://www.crunchbase.com/organization/freemodel}{[crunchbase]}

  \resumeSubheading
    {Esri}{Portland, Oregon}
    {Product Owner, ArcGIS Open Source Apps}{June 2019 -- June 2021}
    \resumeItemListStart
      \item Led a multi-disciplinary team building a portfolio of 14 location based apps across 7 platforms, published in open source. Github community insights reported 100+ daily unique clones, collectively.
      \item Smaller team size required me to adopt multiple roles (Product, Developer, Designer, Docs Writer, GIS Analyst.)
      \item Fostered community as an ArcGIS developer advocate on the ArcGIS for developers website, at Esri flagship events (Developer Summit, User Conference), and at quarterly Meetups in the Portland R\&D center.
    \resumeItemListEnd
    \href{https://developers.arcgis.com/}{[developers.arcgis.com]}

  \resumeSubheading
    {Esri}{Portland, Oregon}
    {iOS Software Engineer, ArcGIS Open Source Apps}{November 2017 -- June 2019}
    \resumeItemListStart
      \item Primary iOS developer of 3 location based apps, published in open source. Engaged with open source community through docs and Github. Published UIs in open source toolkit.
      \item Authored 14+ tutorials teaching how to develop apps using the ArcGIS Runtime API for iOS.
      \item Featured speaker of open source technology products to a crowd of 3K at the 2019 Esri Developer Summit Plenary in Palm Springs, CA.
    \resumeItemListEnd
    \href{https://www.youtube.com/watch?v=yDxsPNwUo9U&t=5s}{[youtube.com]}

  \resumeSubheading
    {Moishe House Foundation}{Remote}
    {iOS Software Engineer \& Technical Team Lead}{July 2015 -- July 2017}
    \resumeItemListStart
      \item Technical lead for org's internal operations software reaching thousands of users annually.
      \item Developed iOS app assisting org with accounting millions (\$) in annual spending on community programming.
      \item Architected mobile API for Ruby on Rails back end.
    \resumeItemListEnd
    \href{https://www.moishehouse.org/}{[moishehouse.org]}

  \resumeSubheading
    {Dot Dot Dash Inc.}{Portland, Oregon}
    {iOS Software Engineer}{June 2014 -- July 2015}
    \resumeItemListStart
      \item Built iOS app controlling LED holiday lights using BLE; lights sold in Apple stores winter 2014 holiday season.
      \item Built iOS camera app to accompany lenses affixable to mobile devices.
      \item Assisted in development and installation of generative, experiential art installations.
    \resumeItemListEnd
    \href{https://www.dotdotdash.io/}{[dotdotdash.io]}

  \resumeSubheading
    {The John F. Kennedy Center for the Performing Arts}{Washington, D.C.}
    {iOS Software Engineer \& Software QA Engineer}{September 2010 -- 2014}
    \resumeItemListStart
      \item QA for digital platform of online arts integrated educational content.
      \item Developed Arts Days Twitter Bot posting engaging tweets daily.
      \item Developed Arts Days iOS App shown in Apple's 2013 WWDC Keynote.
    \resumeItemListEnd
    \href{https://www.kennedy-center.org/education/resources-for-educators/classroom-resources/}{[kennedy-center.org]}

  \resumeSubheading
    {Kibbutz Lotan Center for Creative Ecology}{Hevel Eilot, Israel}
    {Ecological Volunteer}{July 2011 -- November 2011}
    \resumeItemListStart
      \item Assisted research project analyzing the energy efficiency of structures built using earthen materials vs traditional cinderblock; Ben Gurion University.
      \item Learned permaculture and sustainability.
    \resumeItemListEnd
    \href{https://kibbutzlotan.com/en/home-en/}{[kibbutzlotan.com]}

\resumeSubHeadingListEnd

%-----------LIFESTYLE/INTERESTS---------------
\section{Lifestyle \& Interests}
\resumeSubHeadingListStart
  \item Scuba Certified, Wilderness Backpacker, Community Leader, Code Mentor, WIT Advocate, Travel Enthusiast.
\resumeSubHeadingListEnd

\end{document}
